% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Marcel Fiore}
\newcommand{\CVTitle}{Marcel Fiore's Resume}
\newcommand{\CVWebpage}{http://marcelfiore.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={C++, CPP,  Python, Angular, Java, Linux, Get, Perforce, Docker, Scrum, Agile, TDD, OOP, GitFlow, OSI Model},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
Broomfield, CO
\,\SubBulletSymbol\,
720-218-5900
\par
\href{mailto:mf@marcelfiore.com}{mf@marcelfiore.com}
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUMMARY OF QUALIFICATIONS %%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Summary Of Qualifications}
{Summary Of Qualifications}
{PDF:SummaryOfQualifications}

\BulletItem Programming Languages: C++, Python, Angular(JavaScript, HTML, CSS), Java

\Gap
\BulletItem Technologies: Linux (Debian, RedHat), Git, GitLab, CI/CD, Perforce Helix, Docker, REST API

\Gap
\BulletItem Knowledge: Scrum (SAFe), Agile, Test Driven Development, Object Oriented Design, GitFlow, OSI Model


%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Experience}
{Professional Experience}
{PDF:ProfessionalExperience}

\Entry
\href{https://www.caci.com/}{\textbf{CACI}},  Westminster, CO
\hfill
\DatestampYMD{2019}{05}{20} --
\DatestampYMD{2021}{02}{28}
\BulletItem Software Engineer
\begin{Detail}
Mobile Simulator is a new project to CACI which enables testing LTE(4G) and UMTS(3G) without the need for real mobiles, RF, or physical hardware. This enables more efficient testing, automated testing and training of users of the wireless system.
\SubBulletItem Practiced Agile(SAFe) as a member of a team of 9 to develop the Mobile Simulator project.
\SubBulletItem Improved the minutes-long testing process with pysical hardware to a near-instant and automated process.
\SubBulletItem Added new features and fixed bugs in simulator project to meet customer vision using C++, Python, and Angular.
\SubBulletItem Translated detailed specifications including the 3GPP standards into testable code using Test Driven Development.
\SubBulletItem Used GitLab CI/CD to build docker images and automate testing.
\SubBulletItem Developed a tool to easily diagnose Linux devices over USBTTY using Python and Angular.
\end{Detail}

\BigGap
\Entry
\href{https://apolloei.com/}{\textbf{Apollo Enterprise Imaging}},  Fort Collins, CO
\hfill
\DatestampYMD{2018}{08}{01} --
\DatestampYMD{2019}{05}{01}
\BulletItem Developer Intern
\begin{Detail}
\SubBulletItem Maintained an Angular web application that stores and organizes patient medical records.
\SubBulletItem Queried database server to visualize data into graphs on web application.
\end{Detail}

\BigGap
\Entry
\href{http://openwaterfoundation.org/about-owf/staff}{\textbf{Open Water Foundation}},  Fort Collins, CO
\hfill
\DatestampYMD{2018}{06}{01} --
\DatestampYMD{2018}{08}{01}
\BulletItem Web Developer Intern
\begin{Detail}
\SubBulletItem Independently improved screen-size responsiveness of static web pages using CSS and Bootstrap.
\SubBulletItem Sought out and documented JavaScript tools to streamline development of future projects.
\end{Detail}

\BigGap
\Entry
\href{https://www.fioreandsons.com/}{\textbf{Fiore \& Sons, Inc.}},  Denver, CO
\hfill
\DatestampYMD{2017}{05}{01} --
\DatestampYMD{2017}{08}{01}
\BulletItem IT Assistant
\begin{Detail}
\SubBulletItem Expanded VLAN network system to increase internet coverage.
\SubBulletItem Setup and maintained cloud-enabled POE security cameras to ensure coverage of the entire property.
\end{Detail}

%%%%%%%%%%
%% PROJECTS %%
%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}

\Entry
\href{https://gitlab.com/Quellus/libgdx-tower-defense}{\textbf{Tower Defense Game}}
\hfill
Present
\Gap
\begin{Detail}
\SubBulletItem A basic tower defense game written from scratch using Java and the LibGDX graphics library.
\SubBulletItem Written with Object Oriented design patterns.
\end{Detail}

\BigGap
\Entry
\href{https://gitlab.com/Quellus/ncurses-game}{\textbf{Enemy Avoider Game}}
\hfill
\DatestampYMD{2020}{02}{23}
\Gap
\begin{Detail}
\SubBulletItem  Created over 24 hours for the HackCU 2019 hackathon in order to learn the challenges and concepts useful for designing a game engine.
\SubBulletItem A basic enemy avoider game in the command line developed using Ncurses library with C++.
\end{Detail}


\BigGap
\Entry
\href{https://github.com/marcelaf7/Document-Comparison-Program}{\textbf{Document Comparison Program}}
\hfill
\DatestampYMD{2017}{12}{19}
\Gap
\begin{Detail}
 A program that compares documents and searches for a document with a similar subject and user-specified reading level.
\SubBulletItem Designed using C++, Object Oriented Priciples, and the Porter Stemming Algorithm to strip words in different forms down to their root word.
\SubBulletItem Analyzed efficiency and prioritized optimizing searching through large files such as full Shakespeare plays.
\SubBulletItem Created over a semester for Software Development with C++ class at Colorado State University.
\end{Detail}

%%%%%%%%%%
%% Education %%
%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.colostate.edu/}{\textbf{Colorado State University}},  Fort Collins, CO
\hfill
\DatestampYMD{2019}{05}{20}
\begin{Detail}
Bachelor of Science in Computer Science
\end{Detail}

\end{document}
